A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-08-18 talk/talk.tex
Tweaks to talk

@@

\begin{frame}{The Subgraph Isomorphism Problem}

    \centering
    \begin{tikzpicture}%{{{
        \node at (-1, 0) { ~ };
        \node at (9, 0) { ~ };

        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (Na) at (0.75,  0) {1};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (Nb) at (0.75, -1) {2};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (Nc) at (0, -2) {3};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (Nd) at (1.5, -2) {4};

        \node <2> [draw, circle, fill=uofgthistle, inner sep=2pt, font=\bfseries] (Na) at (0.75,  0) {1};
        \node <2> [draw, circle, fill=uofgsunshine, inner sep=2pt, font=\bfseries] (Nb) at (0.75, -1) {2};
        \node <2> [draw, circle, fill=uofglawn, inner sep=2pt, font=\bfseries] (Nc) at (0, -2) {3};
        \node <2> [draw, circle, fill=uofgcobalt, inner sep=2pt, font=\bfseries] (Nd) at (1.5, -2) {4};

        \tikzstyle{edge} = [ultra thick];
        \tikzstyle{ledge} = [color = black!50!white];

        \draw <1> [ledge] (Na) -- (Nb);
        \draw <1> [ledge] (Nb) -- (Nc);
        \draw <1> [ledge] (Nc) -- (Nd);
        \draw <1> [ledge] (Nb) -- (Nd);

        \draw <2> [edge] (Na) -- (Nb);
        \draw <2> [edge] (Nb) -- (Nc);
        \draw <2> [edge] (Nc) -- (Nd);
        \draw <2> [edge] (Nb) -- (Nd);

        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N3) at (5.5, -1) {3};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N4) at (7.5, -1) {4};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N5) at (5.5, -2) {5};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N6) at (7.5, -2) {6};
        \node <1> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N7) at (7.5, -3) {7};

        \node <2> [draw, circle, fill=uofgthistle, inner sep=2pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node <2> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node <2> [draw, circle, fill=uofgsunshine, inner sep=2pt, font=\bfseries] (N3) at (5.5, -1) {3};
        \node <2> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N4) at (7.5, -1) {4};
        \node <2> [draw, circle, fill=uofglawn, inner sep=2pt, font=\bfseries] (N5) at (5.5, -2) {5};
        \node <2> [draw, circle, fill=uofgcobalt, inner sep=2pt, font=\bfseries] (N6) at (7.5, -2) {6};
        \node <2> [draw, circle, fill=white, inner sep=2pt, font=\bfseries] (N7) at (7.5, -3) {7};

        \draw [ledge] (N1) -- (N2);
        \draw [ledge] (N1) -- (N4);
        \draw [ledge] (N2) -- (N4);
        \draw [ledge] (N4) -- (N6);
        \draw [ledge] (N2) to [in=45, out=315] (N7);
        \draw [ledge] (N6) -- (N7);

        \draw <1> [ledge] (N1) -- (N3);
        \draw <1> [ledge] (N3) -- (N5);
        \draw <1> [ledge] (N3) -- (N6);
        \draw <1> [ledge] (N5) -- (N6);
        \draw <2> [edge] (N1) -- (N3);
        \draw <2> [edge] (N3) -- (N5);
        \draw <2> [edge] (N3) -- (N6);
        \draw <2> [edge] (N5) -- (N6);

    \end{tikzpicture}%}}}
    \\~

@@

\begin{frame}{The Basic CP Model}
    \begin{itemize}
        \item One variable for each vertex in the pattern graph, with the domains being the vertices
            of the target graph.
        \item If two vertices are adjacent in the pattern, they must be mapped to adjacent vertices
            in the target.
            \begin{itemize}
                \item In the \emph{induced} variant, non-adjacent vertices must be mapped to
                    non-adjacent vertices. We only discuss the non-induced variant in this talk.
            \end{itemize}
        \item All pattern vertices must be given different values.
        \item Often enhanced: for example, we can filter based upon degree.
    \end{itemize}
\end{frame}

\begin{frame}{Another Perspective}
    \begin{itemize}
        \item The variables describe an injective mapping from the pattern to the target, which
            preserves adjacency.
    \end{itemize}

    \[
        P \rightarrowtail T
    \]
\end{frame}

\begin{frame}{Selected Previous Work}
    \begin{itemize}
        \item VF2: backtracking search, interesting heuristics. \\[0.1cm]
            {\scriptsize A (Sub)Graph Isomorphism Algorithm for Matching Large Graphs. Luigi P.
            Cordella and Pasquale Foggia and Carlo Sansone and Mario Vento. {IEEE} Trans.
        Pattern Anal. Mach. Intell., 2004.}

@@

\begin{frame}{Our Approach}
    \begin{itemize}
        \item Cheaper inference: $10^4$ to $10^6$ recursive calls per second.
        \item Expensive preprocessing once at the top of search, rather than computing distances and
            degree sequences during search.
        \item FC-CBJ instead of MAC:
            \begin{itemize}
                \item A counting-based bit-parallel all-different propagator, which does more
                    than pairwise-$\ne$ AC but less than GAC.
                \item CBJ without explicit conflict sets, and without modifying propagators.
            \end{itemize}
        \item Thread-parallel search:
            \begin{itemize}
                \item Safe, deterministic search via nested parallel folds.
                \item Explicit early work-stealing, to fake discrepancy search.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Supplemental Graphs}
    \only<1> {
        \begin{itemize}
            \item Adjacent vertices must be mapped to adjacent vertices.
            \item Used by SND:
                \begin{itemize}
                    \item Vertices that are distance 2 apart must be mapped to vertices that are within
                        distance 2.
                    \item Vertices that are distance $k$ apart must be mapped to vertices that are within
                        distance $k$.
                \end{itemize}
        \end{itemize}
    }

    \only<2> {
        \begin{itemize}
            \item A subgraph isomorphism

        \[
            f : P \rightarrowtail T
        \]

        is also a subgraph isomorphism

        \[
            f^2 : P^2 \rightarrowtail T^2
        \]

        and a subgraph isomorphism

        \[
            f^3 : P^3 \rightarrowtail T^3
        \]
        \end{itemize}
    }

@@

            \item We construct these graph pairs once, at the top of search, and use them for
                degree-based filtering and during search.

            \item We get lots of implied constraints.
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}{Sequential Experiments}
    \begin{itemize}
        \item 2,487 pairs of instances, selected by other people:
            \begin{itemize}
                \item Real-world graphs.
                \item 2D images and 3D meshes from computer vision applications.
                \item Random (simple, scale-free, 4D mesh, bounded degree).
            \end{itemize}

        \item A mix of satisfiable and unsatisfiable instances, although there is a bias towards
            satisfiable instances\ldots

        \item Up to 900 vertices and 12,410 edges in the pattern, and 5,944 vertices and 34,210
            edges in a target.

        \item Dual Intel Xeon E5-2640 v2 (Q3'13), 64GBytes RAM.

        \item Our code is C++, LAD and VFLib are C, SND is Java.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Parallel Tree-Search}
    \begin{itemize}
        \item Explicit early-first work stealing, to offset incorrect decisions early in search.
            \begin{itemize}
                \item There are EHPs, and this gets rid of them more cheaply than discrepancy
                    searches.
            \end{itemize}
        \item Backjumping is a nested parallel fold with left-zero elements.
        \item Speculative, so we should not expect linear speedups (even on unsat instances).
    \end{itemize}
\end{frame}

\begin{frame}{Sidenote on Safety, Parallelism, and Benchmarking}
    \begin{itemize}
        \item Parallel search will never be substantially worse than sequential search.
        \item Adding more cores will never make things substantially worse (excluding
            hardware weirdness).
        \item Running it twice will give more or less the same runtimes.
        \item All comparisons are against a dedicated sequential implementation of a strong
            algorithm, not a threaded implementation run with one thread.
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \begin{center}
        Reproduce, replicate, or recompute this paper: \\
        \url{http://dcs.gla.ac.uk/~ciaran} \\
        \vspace{1em}
        Tell me whether it worked: \\
        \href{mailto:c.mccreesh.1@research.gla.ac.uk}{\nolinkurl{c.mccreesh.1@research.gla.ac.uk}} \\
        \vspace{1em}
        Donate your subgraph isomorphism problem instances: \\
        \url{http://liris.cnrs.fr/csolnon/SIP.html}
\end{center}
\begin{tikzpicture}[remember picture, overlay]
    \node at (current page.north west) {\begin{tikzpicture}[remember picture, overlay]\fill
    [fill=uofguniversityblue, anchor=north west] (0, 0) rectangle (\paperwidth, -1.5cm);\end{tikzpicture}};
    \node [anchor=north west, shift={(0.2cm,-0.2cm)}] at (current page.north west) {\includegraphics*[keepaspectratio=true,scale=0.5]{UoG_keyline.pdf}};
\end{tikzpicture}
\end{frame}

>>>>

\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{vertexc1/.style={vertex, fill=uofgthistle}}
\tikzset{vertexc2/.style={vertex, fill=uofgpumpkin}}
\tikzset{vertexc3/.style={vertex, fill=uofgpillarbox}}
\tikzset{vertexc4/.style={vertex, fill=uofgturquoise}}
\tikzset{edge/.style={color=black!50!white}}
\tikzset{bedge/.style={ultra thick}}
\tikzset{edged/.style={color=screengrey, dashed}}
\tikzset{edgel3/.style={color=uofgturquoise, ultra thick}}

@@

\begin{frame}{The Subgraph Isomorphism Problem}
    \begin{itemize}
        \item Given a little \emph{pattern} graph and a large \emph{target} graph, find ``a copy
            of'' the pattern inside the target.
    \end{itemize}

    \vspace{2em}

    \centering
    \begin{tikzpicture}
        \node <1> [vertex] (Pc) at (0, 0) { c };
        \node <1> [vertex] (Pd) at (1, 0) { d };
        \node <1> [vertex] (Pb) at (1, 1) { b };
        \node <1> [vertex] (Pa) at (0, 1) { a };

        \node <2> [vertexc1] (Pc) at (0, 0) { c };
        \node <2> [vertexc2] (Pd) at (1, 0) { d };
        \node <2> [vertexc3] (Pb) at (1, 1) { b };
        \node <2> [vertexc4] (Pa) at (0, 1) { a };

        \draw <1> [edge] (Pa) -- (Pb);
        \draw <1> [edge] (Pb) -- (Pc);
        \draw <1> [edge] (Pc) -- (Pd);
        \draw <1> [edge] (Pd) -- (Pb);
        \draw <1> [edge] (Pa) -- (Pc);
        \draw <2> [bedge] (Pa) -- (Pb);
        \draw <2> [bedge] (Pb) -- (Pc);
        \draw <2> [bedge] (Pc) -- (Pd);
        \draw <2> [bedge] (Pd) -- (Pb);
        \draw <2> [bedge] (Pa) -- (Pc);

        \node [anchor=center, font=\huge] at (2.565, 0.5) { $\rightarrowtail$ };

        \node [vertex]   (T1) at (4.13, 0.5) { 1 };
        \node <1> [vertex] (T5) at (5, 0) { 5 };
        \node <1> [vertex] (T6) at (6, 0) { 6 };
        \node <1> [vertex] (T3) at (6, 1) { 3 };
        \node <1> [vertex] (T2) at (5, 1) { 2 };
        \node <2> [vertexc1] (T5) at (5, 0) { 5 };
        \node <2> [vertexc2] (T6) at (6, 0) { 6 };
        \node <2> [vertexc3] (T3) at (6, 1) { 3 };
        \node <2> [vertexc4] (T2) at (5, 1) { 2 };
        \node [vertex]   (T4) at (6.87, 0.5) { 4 };

        \draw [edge]  (T1) -- (T2);
        \draw [edge]  (T1) -- (T5);
        \draw [edge]  (T4) -- (T3);
        \draw [edge]  (T4) -- (T6);
        \draw [edge]  (T2) -- (T6);
        \draw <1> [edge] (T2) -- (T3);
        \draw <1> [edge] (T3) -- (T5);
        \draw <1> [edge] (T5) -- (T6);
        \draw <1> [edge] (T3) -- (T6);
        \draw <1> [edge] (T2) -- (T5);
        \draw <2> [bedge] (T2) -- (T3);
        \draw <2> [bedge] (T3) -- (T5);
        \draw <2> [bedge] (T5) -- (T6);
        \draw <2> [bedge] (T3) -- (T6);
        \draw <2> [bedge] (T2) -- (T5);
    \end{tikzpicture}

@@

\begin{frame}{The Basic CP Model}
    \begin{itemize}
        \item One variable for each vertex in the pattern graph, with the domains being the vertices
            of the target graph.
        \item If two vertices are adjacent in the pattern, their values must be adjacent
            in the target.
            \begin{itemize}
                \item In the \emph{induced} variant, non-adjacent vertices must be mapped to
                    non-adjacent vertices. We only discuss the non-induced variant in this talk.
            \end{itemize}
        \item All pattern vertices must be given different values.
        \item Often enhanced: for example, we can filter based upon degree.
    \end{itemize}
\end{frame}

\begin{frame}{Another Perspective}
    \begin{itemize}
        \item The variables describe an injective mapping from the pattern to the target, which
            preserves adjacency.
    \end{itemize}
\end{frame}

\begin{frame}{Selected Previous Work}
    \begin{itemize}
        \item VF2: backtracking search, interesting heuristics. Widely used. \\[0.1cm]
            {\scriptsize A (Sub)Graph Isomorphism Algorithm for Matching Large Graphs. Luigi P.
            Cordella and Pasquale Foggia and Carlo Sansone and Mario Vento. {IEEE} Trans.
        Pattern Anal. Mach. Intell., 2004.}

@@

\begin{frame}{Our Approach}
    \begin{itemize}
        \item Cheaper inference: $10^4$ to $10^6$ recursive calls per second.
        \item Expensive preprocessing once at the top of search, rather than computing distances and
            degree sequences during search.
        \item FC-CBJ instead of MAC:
            \begin{itemize}
                \item A counting-based all-different propagator, which does more
                    than pairwise-$\ne$ AC but less than GAC.
                \item CBJ without explicit conflict sets, and without modifying propagators.
            \end{itemize}
        \item Bit-parallelism for all major operations.
        \item Thread-parallel search:
            \begin{itemize}
                \item Safe, deterministic search via nested parallel folds.
                \item Explicit early work-stealing, to fake discrepancy search.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Supplemental Graphs}
    \only<1> {
        \begin{itemize}
            \item Adjacent vertices must be mapped to adjacent vertices.
            \item Used by SND:
                \begin{itemize}
                    \item Vertices that are distance 2 apart must be mapped to vertices that are within
                        distance 2.
                    \item Vertices that are distance $k$ apart must be mapped to vertices that are within
                        distance $k$.
                \end{itemize}
        \end{itemize}

        \vspace{1em}

        \centering
        \begin{tikzpicture}
            \node [vertex] (Pc) at (0, 0) { c };
            \node [vertexc2] (Pd) at (1, 0) { d };
            \node [vertex] (Pb) at (1, 1) { b };
            \node [vertexc1] (Pa) at (0, 1) { a };

            \draw [edge] (Pa) -- (Pb);
            \draw [edge] (Pb) -- (Pc);
            \draw [edge] (Pc) -- (Pd);
            \draw [edge] (Pd) -- (Pb);
            \draw [edge] (Pa) -- (Pc);

            \node [anchor=center, font=\huge] at (2.565, 0.5) { $\not\hookrightarrow$ };

            \node [vertexc1] (T1) at (4.13, 0.5) { 1 };
            \node [vertex] (T5) at (5, 0) { 5 };
            \node [vertex] (T6) at (6, 0) { 6 };
            \node [vertex] (T3) at (6, 1) { 3 };
            \node [vertex] (T2) at (5, 1) { 2 };
            \node [vertexc2] (T4) at (6.87, 0.5) { 4 };

            \draw [edge] (T1) -- (T2);
            \draw [edge] (T1) -- (T5);
            \draw [edge] (T4) -- (T3);
            \draw [edge] (T4) -- (T6);
            \draw [edge] (T2) -- (T6);
            \draw [edge] (T2) -- (T3);
            \draw [edge] (T3) -- (T5);
            \draw [edge] (T5) -- (T6);
            \draw [edge] (T3) -- (T6);
            \draw [edge] (T2) -- (T5);

            \node at (5, 2) { ~ };
            \node at (5, -1) { ~ };
        \end{tikzpicture}
        \vspace{1em}
    }

    \only<2> {
        \begin{itemize}
            \item $G^d$ is the graph with the same vertex set as $G$, and an edge between $v$ and $w$ if the distance between $v$ and $w$ in $G$ is
                at most $d$.

            \item For any $d$, a subgraph isomorphism $i : P \hookrightarrow T$ is also a
                subgraph isomorphism $i^d : P^d \hookrightarrow T^d$.
        \end{itemize}

        \vspace{1em}

        \centering
        \begin{tikzpicture}
            \node [vertex] (Pc) at (0, 0) { c };
            \node [vertexc2] (Pd) at (1, 0) { d };
            \node [vertex] (Pb) at (1, 1) { b };
            \node [vertexc1] (Pa) at (0, 1) { a };

            \draw [edge] (Pa) -- (Pb);
            \draw [edge] (Pb) -- (Pc);
            \draw [edge] (Pc) -- (Pd);
            \draw [edge] (Pd) -- (Pb);
            \draw [edge] (Pa) -- (Pc);

            \draw [edgel3] (Pa) -- (Pd);

            \node [anchor=center, font=\huge] at (2.565, 0.5) { $\not\hookrightarrow$ };

            \node [vertexc1] (T1) at (4.13, 0.5) { 1 };
            \node [vertex] (T5) at (5, 0) { 5 };
            \node [vertex] (T6) at (6, 0) { 6 };
            \node [vertex] (T3) at (6, 1) { 3 };
            \node [vertex] (T2) at (5, 1) { 2 };
            \node [vertexc2] (T4) at (6.87, 0.5) { 4 };

            \draw [edge] (T1) -- (T2);
            \draw [edge] (T1) -- (T5);
            \draw [edge] (T4) -- (T3);
            \draw [edge] (T4) -- (T6);
            \draw [edge] (T2) -- (T6);
            \draw [edge] (T2) -- (T3);
            \draw [edge] (T3) -- (T5);
            \draw [edge] (T5) -- (T6);
            \draw [edge] (T3) -- (T6);
            \draw [edge] (T2) -- (T5);

            \draw [edgel3] (T1) to [in=135, out=90] (T3);
            \draw [edgel3] (T1) to [in=225, out=270] (T6);

            \draw [edgel3] (T4) to [in=45, out=90] (T2);
            \draw [edgel3] (T4) to [in=315, out=270] (T5);

            \node at (5, 2) { ~ };
            \node at (5, -1) { ~ };
        \end{tikzpicture}
        \vspace{1em}
    }

@@

            \item We construct these graph pairs once, at the top of search, and use them for
                degree-based filtering at the top of search, and ``adjacency'' filtering during
                search.
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}{Sequential Experiments}
    \begin{itemize}
        \item Dual Intel Xeon E5-2640 v2 (Q3'13), 64GBytes RAM. Our code is C++, LAD and VFLib are C, SND is Java.

        \item 2,487 pairs of instances, selected by other people:
            \begin{itemize}
                \item Real-world graphs.
                \item 2D images and 3D meshes from computer vision applications.
                \item Random (simple, scale-free, 4D mesh, bounded degree).
            \end{itemize}

        \item Up to 900 vertices and 12,410 edges in the pattern, and 5,944 vertices and 34,210
            edges in a target. A mix of satisfiable and unsatisfiable instances, although there is a
            bias towards satisfiable instances\ldots

        \item Please donate your subgraph isomorphism problem instances: \\
            \centering \url{http://liris.cnrs.fr/csolnon/SIP.html}
    \end{itemize}
\end{frame}

@@

\begin{frame}{Parallel Tree-Search}
    \only<1> {
        \centering
        \begin{tikzpicture}[scale=0.75]%{{{
            \coordinate (R);

            \coordinate (N) at (R);

            \coordinate (N1) at ($(N) + (-4, -1.25)$);
            \coordinate (N2) at ($(N) + ( 0, -1.25)$);
            \coordinate (N3) at ($(N) + ( 4, -1.25)$);

            \foreach \na in {1, ..., 3}{
                \coordinate (N\na 1) at ($(N\na) + (-1.25, -1)$);
                \coordinate (N\na 2) at ($(N\na) + ( 0,    -1)$);
                \coordinate (N\na 3) at ($(N\na) + ( 1.25, -1)$);

                \foreach \nb in {1, ..., 3}{
                    \coordinate (N\na\nb t1) at ($(N\na\nb) + (-0.5, -1)$);
                    \coordinate (N\na\nb t2) at ($(N\na\nb) + ( 0.5, -1)$);

                    \coordinate (N\na\nb s1) at ($(N\na\nb) + (-0.3, -0.6)$);
                    \coordinate (N\na\nb s2) at ($(N\na\nb) + ( 0.3, -0.6)$);

                    \coordinate (N\na\nb h1) at ($(N\na\nb) + (-1.5, -3)$);
                    \coordinate (N\na\nb h2) at ($(N\na\nb) + ( 1.5, -3)$);
                }
            }

            \foreach \na in {1, ..., 3}{
                \draw (N) -- (N\na);
                \foreach \nb in {1, ..., 3}{
                    \draw (N\na) -- (N\na\nb);
                }
            }

            \tikzstyle{t} = [draw, fill, fill=uofgcobalt, rounded corners];
            \foreach \na in {1, ..., 3}{
                \foreach \nb in {1, ..., 3}{
                    \draw [t] (N\na\nb) -- (N\na\nb t1) -- (N\na\nb t2) -- cycle;
                }
            }

            \tikzstyle{c} = [draw, circle, fill, fill=uofgcobalt];
            \node [c] at (N) { };

            \foreach \na in {1, ..., 3}{
                \node [c] at (N\na) { };

                \foreach \nb in {1, ..., 3}{
                    \node [c] at (N\na\nb) { };
                }
            }

            \node at (-7, -5.5) { }; \node at (7, -5.5) { };
        \end{tikzpicture}%}}}
    }

    \only<2> {
        \begin{itemize}
            \item Explicit early-first work stealing, to offset incorrect decisions early in search.
                \begin{itemize}
                    \item There are EHPs, and this gets rid of them more cheaply than discrepancy
                        searches.
                \end{itemize}
            \item Backjumping is a nested parallel fold with left-zero elements.
            \item Speculative, so we should not expect linear speedups (even on unsat instances).
        \end{itemize}
    }
\end{frame}

\begin{frame}{Sidenote on Safety, Parallelism, and Benchmarking}
    \begin{itemize}
        \item We guarantee:
            \begin{itemize}
                \item Parallel search will never be substantially worse than sequential search.
                \item Adding more cores will never make things substantially worse (excluding
                    hardware weirdness).
                \item Running it twice will give more or less the same runtimes.
            \end{itemize}
        \item All comparisons are against a dedicated sequential implementation of a strong
            algorithm, not a threaded implementation run with one thread.
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \begin{center}
        Reproduce, replicate, or recompute this paper: \\
        \url{http://dcs.gla.ac.uk/~ciaran} \\
        \vspace{1em}
        Tell me whether it worked: \\
        \href{mailto:c.mccreesh.1@research.gla.ac.uk}{\nolinkurl{c.mccreesh.1@research.gla.ac.uk}} \\
        \vspace{1em}
        \item Donate your subgraph isomorphism problem instances: \\
        \url{http://liris.cnrs.fr/csolnon/SIP.html}
    \end{center}

\begin{tikzpicture}[remember picture, overlay]
    \node at (current page.north west) {\begin{tikzpicture}[remember picture, overlay]\fill
    [fill=uofguniversityblue, anchor=north west] (0, 0) rectangle (\paperwidth, -1.5cm);\end{tikzpicture}};
    \node [anchor=north west, shift={(0.2cm,-0.2cm)}] at (current page.north west) {\includegraphics*[keepaspectratio=true,scale=0.5]{UoG_keyline.pdf}};
\end{tikzpicture}
\end{frame}
